---
title: "R Markdown and Plotly"
subtitle: "Food Consumption in UK"
author: "Rafael Gurgel"
date: "31/01/2018"
output: ioslides_presentation
fontsize: 8pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(plotly)
```

## Introduction
This presentation is the Week 3 Assignment for the course Developing Data Products on Coursera.

We'll analyse the average comsumption (in grams per person, per week) of 17 types of food in the four countries in the UK in 1997 (Source: DEFRA). This data is a classical PCA example. 

On the next slide, we'll check the consumption by countries. If you click on the countries legend you can hide/show their bars!!! 

You can check the code [here](https://github.com/rafagurgel/DDP_Week03_Assignment)


## Food Consumption

```{r, fig.height=5}
food <- read.csv('food_consumptionUK.csv')
food<- food %>% arrange(Food)
rownames(food) <- food[,1]
food <- food[,-1]
names(food) <- gsub('_','\\.', names(food))
food.names <- factor(rownames(food), levels = rownames(food))
food.var <- apply(food, 1, var)
plot_ly(x = food[,1], name =  names(food)[1], y = paste(food.names,' '), type = 'bar', orientation = 'h',
        marker = list(line = list(color = 'rgb(0, 0, 0)', width = 0.75)))%>%
  add_trace(x = food[,2], name =  names(food)[2]) %>%
  add_trace(x = food[,3], name =  names(food)[3]) %>%
  add_trace(x = food[,4], name =  names(food)[4]) %>%
  layout(title = 'Average Food Consumption in grams per person per year ',
         legend = list(orientation = 'h'),
         yaxis = list(title = '',
                      showgrid = FALSE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      zeroline = FALSE,
                      autorange = 'reversed',
                      tickfont = list(size = 10)),
         xaxis = list(showgrid = T,
                      showline = T,
                      showticklabels = T,
                      zeroline = T,
                      tickfont = list(size = 10)),
         margin = list(l = 110, r = 20, t = 40, b = 10))
```